\problemname{Interval Product}
%\illustration{.5}{filename}{Image by \href{url}{Author}}

There is an array of $N$ positive integers, $x_1, x_2, ... x_N$.
Your friend gives you $Q$ queries, which can be:
\begin{itemize}
\item {\tt q l r} : Consider the product $P = x_l \times x_{l+1} \times ... \times x_{r-1} \times x_r$. How many trailing zeroes are there in the binary representation of $P$? (Yay! Your friend no longer cares about the product being positive, negative, or zero.)
\item {\tt s i v} : Set the value of $x_i$ to $v$.
\end{itemize}
Since your friend have a large number of queries, you have to find a way to answer them efficiently.

\section*{Input}
The first line of the input has an integer $T$, the number of test cases.\\
Each case has two integer $N, Q$ on the first line.\\
The next line has $N$ integers, $x_1, x_2, ... x_N$.\\
Each of the next $Q$ lines gives a query, which can be one of the two types introduced above.

\section*{Output}

For each query of the first type, output the number of trailing zeroes in the binary representation of the interval product.

\section*{Constraints}
\begin{itemize}
\item $1 \leq T\leq 15$
\item $1 \leq N, Q \leq 10^5$
\item $1 \leq l \leq r \leq N$ for all queries of the first type. $1 \leq i \leq N$ for all queries of the second type.
\item It is guaranteed that $1 \leq x_i \leq 10^9$ for $1 \leq i \leq N$ before the first query and after every query is processed.
\end{itemize}

\section*{Subtasks}
\begin{itemize}
\item (Small - 20 points): There are only queries of the first type. That is, there will be no changes on the array.
\item (Large - 30 points): Original constraints.
\end{itemize}

Note that the last sample case will not appear in the {\it Small} subtask, as it contains queries of the second type.

\section*{Hint}
The number of trailing zeroes in the binary representation of a decimal integer $P$ equals how many times $P$ can be evenly divided by 2. For example, $44 = (101100)_2$ has two trailing zeroes and can be evenly divided at most twice: $44 / 2 = 22$, $22 / 2 = 11$, and $11$ is odd.