\problemname{Cryptic City}
%\illustration{.5}{filename}{Image by \href{url}{Author}}

You entered a {\bf cryptic city} in your dream.
The city is {\tt very large} and has a complicated road network.
There are $N - 1$ intersections in the city, numbered from $2$ to $N$ (Strangely there is no intersection $1$).
The roads in the city are constructed in a cryptic manner.
Between each pair of intersections $x$ and $y$ ($x \neq y$), there exists a bidirectional road of length {\it GCD}$(x, y)$.
You are now at intersection $A$ and want to go to intersection $B$.
What is the shortest path you can take from $A$ to $B$?

\section*{Input}

The first line of the input has an integer $T$, the number of test cases.\\
Each case has three integers $N, A, B$ on a single line.

\section*{Output}

For each case, output the shortest path your can take from $A$ to $B$. The shortest path is written as a sequence of visited intersections (including $A$ and $B$), separated by single spaces. If there are multiple possible shortest paths, you may output any of them.

\section*{Constraints}
\begin{itemize}
\item $1 \leq T\leq 30$
\item $3 \leq N \leq 10^6$
\item $2 \leq A, B \leq N$
\item $A \neq B$
\end{itemize}

\section*{Subtasks}
\begin{itemize}
  \item $N \leq 50$
  \item Original constraints
\end{itemize}

\section*{Note}
There are $O(N^2)$ roads in the city. In the {\it large} subtask, an algorithm that processes every road will be too slow, and you will not be able to store all the roads in memory.\\

\noindent In the first sample case, the shortest path goes directly from intersection $4$ to intersection $6$. The road between them has length {\it GCD}$(4, 6) = 2$. Note that there exist multiple possible answers. You only need to find a path that minimizes the total distance travelled. You do {\it NOT} need to minimize the number of intersections visited. For the first sample case, ``{\tt 4 5 6}'' will also be accepted, as {\it GCD}$(4, 5)$ + {\it GCD}$(5, 6) = 1 + 1 = 2$.\\

\noindent The last two sample cases will not appear in the {\it small} subtask.\\
